\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
Update on Overleaf.

A cost and a duration function are associated to each action.  The duration
function provides a duration interval for the action achievement and is used, in
one hand, to schedule the different streams and, on the other hand, as an
additional cost function. Cost here is not used here to estimate only standard time and energy consumption but
to estimate a number factors that measure the satisfaction of the human in terms of acceptabiliof human based not

>>>>

A cost and a duration function are associated to each action.  The duration
function provides a duration interval for the action achievement and is used, in
one hand, to schedule the different streams and, on the other hand, as an
additional cost function. Cost here is not used here to estimate only standard time and energy consumption but
to estimate a number factors that measure the satisfaction of the human in terms of acceptability and legibility of robot behavior.
